\documentclass[10pt, a4paper]{article}

\usepackage[a4paper, top=0.8cm, bottom=0.8cm, left=1.2cm, right=1.2cm]{geometry}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\babelfont{rm}{Arial}

\definecolor{primary}{RGB}{0, 0, 0}
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt} 
\setlist[itemize]{noitemsep, topsep=1pt, partopsep=0pt, parsep=0pt, leftmargin=1.2em}

\begin{document}

\begin{center}
    {\Huge \textbf{SHANKAR PRASAD TN}} \\
    \vspace{1pt}
    \small
    Bangalore, India \textbullet{} +91-7411146096 \textbullet{} \href{mailto:shankarprasadtn@gmail.com}{shankarprasadtn@gmail.com} \textbullet{} \href{https://shankarprasadtn.xyz}{shankarprasadtn.xyz} \\
    \href{https://linkedin.com/in/shankar-prasad-34853288}{linkedin.com/in/shankar-prasad-34853288} \textbullet{} \href{https://github.com/shankarprasadtn}{github.com/shankarprasadtn}
\end{center}

\section{Professional Summary}
Dynamic IT Professional with 8+ years of experience in enterprise infrastructure and systems administration, currently transitioning into a Multi-Cloud DevOps role. Specialized in implementing scalable CI/CD pipelines, orchestrating containers with Kubernetes and Docker, and automating cloud security via Python (Boto3). Recently upskilled through a PG program in Multi-Cloud Architecture and Generative AI (2026), aiming to bridge veteran infrastructure reliability with modern DevOps agility.

\section{Technical Skills}
\begin{itemize}
    \item \textbf{Cloud Platforms:} AWS (EC2, S3, Lambda, IAM, VPC), Azure (AZ-104), Multi-Cloud Architecture.
    \item \textbf{DevOps \& Orchestration:} Kubernetes (K8s), Docker, CI/CD Pipelines, Git/GitHub, JIRA.
    \item \textbf{Operating Systems:} CentOS, Ubuntu, Windows Server 2026, Windows 11/10, WSL2.
    \item \textbf{Automation \& AI:} Python (Boto3), Shell Scripting, Agentic AI, GenAI Integration, AWS Lambda, Microservices.
    \item \textbf{Infrastructure \& Admin:} Active Directory, MDT, Lansweeper, Snipe-IT, EARS, Office 365, Exchange.
    \item \textbf{Networking \& Security:} VPN, Cisco Meraki, Aruba Switches, Firewall Configuration, CCNA.
\end{itemize}

\section{Professional Experience}

\textbf{UPS Logistics Pvt Ltd - ITC} \hfill Jul 2022 -- Present \\
\textit{Management Specialist} \hfill Bangalore, Chennai
\begin{itemize}
    \item Orchestrate IT incident/change workflows using JIRA, improving service delivery efficiency by 20\%.
    \item Administer Microsoft Azure subscription resources, managing Entra ID (Azure AD), hybrid directory synchronization, and RBAC policies.
    \item Deploy OS images using Cosmic Systems/MDT; distribute applications via GSDP and Group Policy.
    \item Manage IT assets and compliance using Lansweeper and EARS across Azure, O365, and Exchange Admin Center.
    \item \textbf{Key Achievement:} Successfully led IT infrastructure setup for the India Technology Center (ITC) in Chennai.
\end{itemize}

\textbf{V2Soft Pvt Ltd (Client: STTAS-A UPS Company)} \hfill Dec 2020 -- Jul 2022 \\
\textit{IT System Administrator} \hfill Bangalore, India
\begin{itemize}
    \item Configured WSL2 with Ubuntu and Docker for containerized development and testing environments.
    \item Operated IT asset management tools (Snipe-IT, Lansweeper) and managed Symantec Endpoint consoles.
    \item Executed patch management cycles using WSUS in coordination with information security policies.
\end{itemize}

\textbf{Digicom Systems Ltd (Clients: AO Smith, Exotel Ltd)} \hfill Apr 2019 -- Nov 2020 \\
\textit{Systems Engineer} \hfill Bangalore, India
\begin{itemize}
    \item Executed server migrations to cloud environments and provisioned VMs via Cisco HyperFlex.
    \item Administered backups and disaster recovery using CommVault, Veritas, and EMC Avamar.
\end{itemize}

\textbf{Wipro Ltd} \hfill Mar 2017 -- Mar 2019 \\
\textit{Senior Associate Engineer} \hfill Bangalore, India
\begin{itemize}
    \item Managed Active Directory (user provisioning, security groups) and resolved complex network issues.
\end{itemize}

\section{Project Portfolio}

\textbf{Gratitude App (Capstone)} \textbullet{} \textit{Multi-Cloud CI/CD} \\
Implemented a multi-cloud architecture and CI/CD pipeline to deploy a collaborative application across AWS and Azure.

\textbf{Asset QR Management (v1.2.3)} \textbullet{} \textit{Inventory Automation} \\
Developed a QR-based tracking system to streamline inventory management and hardware lifecycle visibility.

\textbf{My Travel Memory} \textbullet{} \textit{Web Development} \\
Designed and developed a personal travel logging application to capture and organize travel experiences.

\textbf{Microservices on Containerization} \textbullet{} \textit{Docker \& Orchestration} \\
Decoupled application architecture into microservices and deployed them using Docker containers.

\textbf{Cloud Security Monitor} \textbullet{} \textit{Automation} \\
Built an automated tool using Boto3 to detect unencrypted S3 buckets, enhancing cloud data protection.

\section{Education \& Certifications}
\begin{itemize}
    \item \textbf{PG Program in Multi-Cloud Architecture \& DevOps} -- Hero Vired \hfill 2026
    \item \textbf{BE in Computer Science} -- CMRIT, Visveshwaraya Technological University \hfill 2016
    \item \textbf{Diploma in CS} -- Bharath Polytechnic \hfill 2009 -- 2012
    \item \textbf{Certifications:} AZ-104, CCNA, MCITP, CompTIA A+.
\end{itemize}

\end{document}